Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2018-09-15 paper/drafts/draft_final.tex
updated paper

	There has been an enormous strive to develop methods to obtain a closed loop control system for MAV's. The methods range from estimation to sensing based on different vectors. The majority of the estimation based controls rely on the voltage or current draw by the motors. Mahoney et al \cite{Mahoney1} devised such a system which estimates the thrust using a for loop based calculation of the thrust. This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible. As well their system requires heavy calibration and would not be easily transferable between systems. Similarly Awan et al \cite{awan} developed an adaptive observer based thrust estimation system. This method allowed for the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation. The main issue along this method is that their paper only accounts for hover not flight, as well their models were based around a linearized system and any nonlinear disturbances would cause errors in their system. In contrast Sydney et al \cite{sydney} developed a highly complex system where they modeled the entire system, both linear and nonlinear. By doing so their

@@

	There are certain limitations within our setup that we have to address. The first of which is the low range of the wind sensor which can maximally measure only $25%$ of the motor's maximum RPM. The other major shortcoming of our paper is the static nature of the experiments. Our tests have only been in a fixed and controlled environment, with only one motor as the test. In real situations on a quadrotor or such, the behaviour of our system might be significantly different.

	low wind speed. Have not accounted for multiple sources of wind. fixed and controlled environment. only one propeller. 
	\section{5}
	\subsection{Reiteration of results}
	In this paper we presented a closed loop control system for the purposes of controlling MAV rotor systems by the introduction of a hot wire anemometer. The anemometer measures the rate of wind flow from the downwash of the MAV rotor and there is a linear relationship that is developed between wind flow velocity and the thrust output of the system. Through this relationship we developed a PI controller that maintains a desired thrust value against internal and external disturbances.
	\subsection{Reiteration of applications}

>>>>

	There has been an enormous strive to develop methods to obtain a closed loop control system for MAV's. The methods range from estimation to sensing based on different vectors. The majority of the estimation based controls rely on the voltage or current draw by the motors. Mahoney et al \cite{mahoney1} devised such a system which estimates the thrust using a for loop based calculation of the thrust. This system while it allows for a valid estimation of the thrust, it is a complex system that requires relatively heavy computation and therefore is not feasible. As well their system requires heavy calibration and would not be easily transferable between systems. Similarly Awan et al \cite{awan} developed an adaptive observer based thrust estimation system. This method allowed for the MAV to maintain a hover with higher precision compared to previous methods involving thrust estimation. The main issue along this method is that their paper only accounts for hover not flight, as well their models were based around a linearized system and any nonlinear disturbances would cause errors in their system. In contrast Sydney et al \cite{sydney} developed a highly complex system where they modeled the entire system, both linear and nonlinear. By doing so their

@@

	There are certain limitations within our setup that we have to address. The first of which is the low range of the wind sensor which can maximally measure only $25\%$ of the motor's maximum RPM. The other major shortcoming of our paper is the static nature of the experiments. Our tests have only been in a fixed and controlled environment, with only one motor as the test. In real situations on a quadrotor or such, the behaviour of our system might be significantly different.  	
	low wind speed. Have not accounted for multiple sources of wind. fixed and controlled environment. only one propeller. 
	\section{5}
	\subsection{Reiteration of results}
	In this paper we presented a closed loop control system for the purposes of controlling MAV rotor systems by the introduction of a hot wire anemometer. The anemometer measures the rate of wind flow from the downwash of the MAV rotor and there is a linear relationship that is developed between wind flow velocity and the thrust output of the system. Through this relationship we developed a PI controller that maintains a desired thrust value against internal and external disturbances.
	\subsection{Reiteration of applications}
